%!TEX root = TTK4215-Summary.tex
\section{Preliminaries}
\subsection{Norms}
\paragraph{General $p$-norm}
\begin{equation}
	||x||_p
	=
	\left(
		\int_{0}^{\infty} |x(\tau)|^p \dif t
	\right)
	^{1/p}
\end{equation}

\paragraph{$\mathcal{L}_\infty$-norm}
\begin{equation}
	||x||_\infty
	=
	\sup_{t \geq 0} |x(t)|
\end{equation}
and we say $x \in \mathcal{L}_\infty$ when $||x||_\infty$ exists.

%!TEX root = TTK4215-Summary.tex
\subsection{Models for dynamic systems}

\begin{equation}
	\V{\dot{x}}
	=
	\M{A} \V{x}
	+
	\M{B} \V{u}
\end{equation}

\begin{equation}
	\V{y}
	=
	\M{C}\T \V{x}
\end{equation}

\paragraph{Controllability}
\begin{equation}
	\M{P}_c
	\triangleq
	\begin{bmatrix}
		\M{B} \\ \M{AB} \\ \vdots \\ \M{A}^{n-1}\M{B}
	\end{bmatrix}
\end{equation}

If $\M{P}_c$ is nonsingular, the system is controllable, and can be transformed to the \emph{controllability canonical form} by
\begin{equation}
	\V{x}_c
	=
	\M{P}_c^{-1} \V{x}
\end{equation}

\paragraph{Properness}
A transfer function $\M{G}(s) = \frac{\M{N}(s)}{\M{D}(s)}$ is
\begin{itemize}
	\item \emph{proper} if $\deg(\M{N}) \leq \deg(\M{D})$,
	\item \emph{biproper} if $\deg(\M{N}) = \deg(\M{D})$,
	\item \emph{stricly proper} if $\deg(\M{N}) < \deg(\M{D})$.
\end{itemize}

\subsection{Transfer function properties}
Consider the polynomial
\begin{equation}
	X(s) = \alpha_n s^n + \alpha_{n-1} s^{n-1} + \cdots + \alpha_0
\end{equation}
and the transfer function
\begin{equation}
	G(s) = \frac{Z(s)}{R(s)}
	.
\end{equation}

\paragraph{Monic:} $X(s)$ is \emph{monic} iff $\alpha_n = 1$.

\paragraph{Hurwitz:} $X(s)$ is \emph{Hurwitz} if all roots of $X(s) = 0$ are in the left half plane.

\paragraph{Minimum phase:} A system defined by the t.f. $G(s)$ is \emph{minimum phase} iff $Z(s)$ is Hurwitz.

\paragraph{Stability:} A system defined by the t.f. $G(s)$ is \emph{stable} if $R(s)$ is Hurwitz.

\paragraph{Coprime:} Two polynomials are \emph{coprime} if they have no common factors other than a constant.

\subsection{(Strictly) positive real transfer functions}

\paragraph{KYP Lemma}
Given a square matrix $A$ with eigenvalues $\Re(\lambda) \leq 0$, a vector $B$ such that $(A,B)$ controllable, a vector $C$, and scalar $d \geq 0$, then the t.f.
\begin{equation}
	G(s) = d + C\T (s \mathrm{I} - A)^{-1} B
\end{equation}
is PR iff $\exists$ a symmetric pos. def. matrix $P$ and a vector $q$ such that
\begin{gather}
	A\T P + P A = -q q\T \\
	P B - C = \pm \sqrt{2d} \cdot q
	.
\end{gather}

\paragraph{LKY Lemma}
Given a stable matrix $A$, a vector $B$ such that $(A,B)$ controllable, a vector $C$ and a scalar $d \geq 0$, then the t.f.
\begin{equation}
	G(s) = d + C\T (s \mathrm{I} - A)^{-1} B
\end{equation}
is SPR iff for any pos. def. matrix $L$, $\exists$ a symmetric pos. def. matrix $P$, a scalar $\nu > 0$ and a vector $q$ such that
\begin{gather}
	A\T P + P A = -q q\T - \nu L \\
	P B - C = \pm q \sqrt{2d}
	.
\end{gather}

\paragraph{MKY Lemma}
Given a stable matrix $A$, vectors $B,C$, and a scalar $d \geq 0$, we have: If
\begin{equation}
	G(s) = d + C\T (s \mathrm{I} - A)^{-1} B
\end{equation}
is SPR, then for any $L = L\T > 0$, $\exists$ a scalar $\nu > 0$, a vector $q$ and a $P = P\T > 0$ such that
\begin{gather}
	A\T P + P A = -q q\T - \nu L \\
	P B - C = \pm q \sqrt{2d}
	.
\end{gather}